Duplicate Question Detection using Online Learning

### 2016-11-24 paper/main.tex
draft paper

\begin{center}
 \begin{tabular}{|l c c |} 
 \hline
 Dataset & \#Similar Label & \#All \\ [0.5ex] 
 \hline\hline
 Training Stackoverflow & 1238 & 62499 \\ 
 \hline
 Testing Stackoverflow & 258 & 10398  \\
 \hline
 Training Reddit & 114 &   676 \\
 \hline
 Testing Reddit & 23 & 139  \\
 \hline
\end{tabular}
\end{center}

@@

\emph{How effective is our approach?}

@@

\emph{What variables are important in our modelling routine, does it vary with different data sources?}

\begin{figure}[ht]
\caption{Variable importance for the various text features for our Stack overflow model}
\centering
\includegraphics[width=0.4\textwidth]{so_varimp.png}
\end{figure}

\begin{figure}[ht]
\caption{Variable importance for the various text features for our Reddit model}
\centering
\includegraphics[width=0.4\textwidth]{reddit_varimp.png}
\end{figure}

From the two images of the variable importance metrics, it is clear that using different models will yield different parameter weightings. More importantly it reveals that LDA features appear to be the most significant. This also suggests that features which may incorporate information around the subject of the post may also improve performance. Recently including features like POS tags and named-entities have been used to great effect in information retrieval problems\cite{featurerich}.

\emph{What is the effect of changing the types of models used}

When examining the different models, linear models and tree models were compared and contrasted. We achieved better results from using tree based models like random forest due to the interaction between the different features. Since different models have different parameters weights, having a tree-based model makes it easier to achieve reasonable results rather than needing to tune and fine the relevant interactions in the linear model framework.

@@

Threats include the ability of this approach to generalise to all young communities. As young communities is quite broad, the focus in this paper has been quite targeted, looking at computer science forums, and learning centers. The duplicate questions were also quite targeted and manually pruned.

The model also struggled on longer posts as the features did not appear to pick up the subject of the post correctly.

Threats to construct validity - suitability of evaluation metrics. In recent years ROUGE metric has been created for information retrieval problems, especially when reconstructing answers to be aligned with a human answer. These are based on the recall metric with noticeable improvements. In future interations which focus more on how the answer is presented, would definitely focus on using this instead

\section{Related Work}

Zhang \emph{et al}\cite{dupred}

Besides what has been in the proposal, links to online learning, such as vowpal wabbit:

Chopra \emph{et al}\cite{simmatrix}

@@

% insert some link to some paper
Text summarization - longer texts means similarity breaks down really aggressively which can lead to better evaluation metrics such as ROGUE.

@@

Some conclusion

@@

>>>>

\begin{table}[h!]
\centering
\caption{Statistics of the Training and the Test Set.}
 \begin{tabular}{|l c c |}
 \hline
 Dataset & \#Similar Label & \#All \\ [0.5ex]
 \hline\hline
 Training Stackoverflow & 1238 & 62499 \\
 \hline
 Testing Stackoverflow & 258 & 10398  \\
 \hline
 Training Reddit & 114 &   676 \\
 \hline
 Testing Reddit & 23 & 139  \\
 \hline
\end{tabular}

\hfill \break

Note: \#Duplicate refers to the number of duplicate questions. \#All refers to the total number of questions.
\end{table}

@@

\subsubsection{How effective is our approach}

The recall rate for both datasets is shown below

\begin{table}[h!]
\centering
\caption{Recall rate for both datasets.}
 \begin{tabular}{|l r |}
 \hline
 Dataset & Recall Rate  \\ [0.5ex]
 \hline\hline
 Stackoverflow & 76.87\%  \\
 \hline
 Reddit & 80.59\%  \\
 \hline
\end{tabular}

\end{table}

@@

For example question answers below are two relatively common questions with the curated answer by the community.

\begin{itemize}
    \item \emph{Will I get admitted?} We certainly can give you some feedback on this topic. However, we are not the admissions committee. We do not know exactly how decisions are made, so no one is liable here for your admissions status in the end.
    \item \emph{Why was I rejected?	} We can not answer that for you here. We can, however, give you advice for the future.
\end{itemize}

However in both instances the answer is not helpful for the end-user, and likely to be regarded as a low quality response.

\subsubsection{What variables are important in our modelling routine, does it vary with different data sources}

The figures 1 and 2 demonstrate the variable importance metrics, it is clear that using different models will yield different parameter weightings. More importantly it reveals that LDA features appear to be the most significant. This also suggests that features which may incorporate information around the subject of the post may also improve performance. Recently including features like POS tags and named-entities have been used to great effect in information retrieval problems\cite{featurerich}.

\begin{figure}[ht]
\centering
\caption{Variable importance for the various text features for our Stack overflow model}
\includegraphics[width=0.4\textwidth]{so_varimp.png}
\end{figure}

\begin{figure}[ht]
\centering
\caption{Variable importance for the various text features for our Reddit model}
\includegraphics[width=0.4\textwidth]{reddit_varimp.png}
\end{figure}

\subsubsection{What is the effect of changing the types of models used}

When examining the different models, linear models and tree models were compared and contrasted. We achieved better results from using tree based models like random forest due to the interaction between the different features. Since different models have different parameters weights, having a tree-based model makes it easier to achieve reasonable results rather than needing to tune and fine the relevant interactions in the linear model framework as shown by Elith \emph{et al}\cite{gbminteraction}.

\begin{table}[h!]
\centering
\caption{Recall rate for both datasets using different supervised models.}
 \begin{tabular}{|l l r|}
 \hline
 Dataset & Model & Recall Rate  \\ [0.5ex]
 \hline\hline
 Stackoverflow & Random Forest & 76.87\%  \\
 Stackoverflow & Logistic Regression & 37.12\%  \\
 \hline
  Reddit & Random Forest & 80.59\%  \\
  Reddit & Logistic Regression & 10.84\%  \\
 \hline
\end{tabular}
\end{table}

@@

Threats include the ability of this approach to generalise to all young communities. As young communities is quite broad, the focus in this paper has been quite targeted, looking at computer science forums, and learning centers. The duplicate questions were also targeted and manually pruned.

Threats to construct validity - suitability of evaluation metrics. In recent years ROUGE (Recall-Oriented Understudy for Gisting Evaluation)\cite{rouge} metric has been created for information retrieval problems, especially when reconstructing answers to be aligned with a human answer. These are based on the recall metric with noticeable improvements. In future iterations which focus more on how the answer is presented, would definitely focus on using this instead.

\section{Future Work}

As outlined in how this model was put together not all components are subject to online learning. More specifically the supervised portion used only batch learning techniques. Future work would examine using online supervised learning to augment this model as shown in Vowpal Wabbit\cite{vowpalwabbit}.

Within the Gensim library, the similarity matrix used was the cosine similarity. Chopra \emph{et al}\cite{simmatrix} has demonstrated that this measure of distance can be improved by learning different measures of similarity through utilizing weights within a Neural Network.

@@

% insert some link to some paper
%Text summarization - longer texts means similarity breaks down really aggressively which can lead to better evaluation metrics such as ROGUE.

@@

In this paper we proposed a way to perform duplicate detection using online learning for Stack Overflow and Reddit. This approach measures similarity of two posts by comparing their observable factors, such as the titles, description and tags and their latent factors corresponding to the topic distribution that are learned from the natural language description of the question. Our approach also constructs other feature encodings including LSI and word2vec.

We evaluated this approach using data available from Stack Overflow and Reddit which lead to experimental results of recall rates above 75\%.

In the future we plan to extend this approach with bleeding edge techniques such as feature rich-encoding to develop better techniques to improve the effectiveness of this approach.

@@

\bibitem{gbminteraction}
Elith J. and Leathwick J. (2016). ``Boosted Regression Trees for ecological modelling'' Retreived on 24 November from \url{https://cran.r-project.org/web/packages/dismo/vignettes/brt.pdf}

\bibitem{vowpalwabbit}
Agarwal A., Chapelle O., Dudik M. and Langford J. (2012). ``A Reliable Effective Terascale Linear Learning System''. In Journal of Machine Learning Research 2012. Retreived on 24 November from \url{https://arxiv.org/pdf/1110.4198v3.pdf}

\bibitem{rouge}
Lin CY. (2004). ``ROUGE: A Package for Automatic Evaluation of Summaries''. In Proceedings of the Workshop on Text Summarization Branches Out (WAS 2004), Barcelona, Spain, July 25 - 26, 2004. Retreived on 24 November from \url{http://www.aclweb.org/anthology/W/W04/W04-1013.pdf}
